---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = FALSE)

require("knitr")
opts_knit$set(root.dir = 'D:/defne/Documents/BC/TVO/TnSeq_RNASeq_Evo/New Experiments/')
```

Basic set up
```{r}
exptsheet <- read.csv('exptsheet121319.csv', header=T, stringsAsFactors = F)

annot <- read.csv('Annotation_3Strains_Cleaned.csv', header=T, stringsAsFactors = F)
annot_base <- annot[,c('D39.old', 'TIGR4.old', 'TAIWAN.19F.old')]


source('Entropy/threshold_classify.R')
source('D:/defne/Documents/BC/TVO/Metabolic Models/RCC analysis/T4/RCC_functions/make_RNAseq_df.R')

library(caret)

library(PRROC)
```


## Single timepoint entropy
```{r}
for (i in c(1:nrow(exptsheet))){
  #read the data
  rnaseqfile <- exptsheet$RNAseqFile[i]
  RNAseq <- read.csv(rnaseqfile, 
                   header=T, stringsAsFactors=F)
  RNAseq$log2FoldChange<- as.numeric(as.character(RNAseq$log2FoldChange))
  #compute entropy
  exptsheet$H.DE[i] <- log(2*pi*exp(1)*var(RNAseq$log2FoldChange, na.rm=T))
}

H_single <- exptsheet
H_single$Survive <- as.logical(H_single$Survive)
#using Gorup=="Train" as training set and Grou=="Test/Test2" as test
entropy_1tp_classifier <- threshold_classify(H_single$H.DE[H_single$Group=='Train'],
                                          as.factor(H_single$Survive[H_single$Group=='Train']))
H.t <- entropy_1tp_classifier$threshold
H_single$Prediction <- H_single$H.DE<H.t
write.csv(H_single[,c(2:7,9,12:16)], 'Dec19/NewDataDec19_code/H1tp_predictions.csv', row.names=F)

# record threshold and confusion matrices
sink('Dec19/NewDataDec19_code/H1tp_CMs.txt')
cat("Threshold: ")
cat(H.t)
cat("\n\n\nTRAINING SET\n")
confusionMatrix(as.factor(H_single$Prediction)[H_single$Group=="Train"], as.factor(H_single$Survive[H_single$Group=="Train"]), positive = "TRUE")
cat("\n\n\nTEST SET\n")
confusionMatrix(as.factor(H_single$Prediction)[H_single$Group!="Train"], as.factor(H_single$Survive[H_single$Group!="Train"]), positive = "TRUE")
sink()


#line plot Fig 4E
ggplot(H_single[H_single$Group=='Train',], aes(x=Time, y=H.DE, group=Experiment, col=Survive))+geom_line()+
  geom_hline(yintercept = H.t, col='red',linetype = "dashed" )+
  facet_wrap(.~AB, ncol=4)+theme_bw()+labs(y="Entropy")
ggsave('Dec19/NewDataDec19_code/H1tp_train_lineplot.svg', width=8, height=5, units="in")

ggplot(H_single[H_single$Group!='Train',], aes(x=Time, y=H.DE, group=Experiment, col=Survive))+geom_line()+
  geom_hline(yintercept = H.t, col='red',linetype = "dashed" )+
  facet_wrap(.~AB, ncol=4)+theme_bw()+labs(y="Entropy")
ggsave('Dec19/NewDataDec19_code/H1tp_test_lineplot.svg', width=8, height=5, units="in")


# ROC and PR curves
roc_train <- roc.curve(H_single$H.DE[H_single$Survive=="FALSE" & H_single$Group=="Train"],
                       H_single$H.DE[H_single$Survive=="TRUE" & H_single$Group=="Train"], curve=TRUE)
roc_test <- roc.curve(H_single$H.DE[H_single$Survive=="FALSE" & H_single$Group!="Train"],
                       H_single$H.DE[H_single$Survive=="TRUE" & H_single$Group!="Train"], curve=TRUE)

svg('Dec19/NewDataDec19_code/H1tp_ROC.svg')
plot(roc_train, color="black", main="Single timepoint model", auc.main = FALSE)
plot(roc_test, color="red", add=TRUE)
dev.off()


pr_train <- pr.curve(H_single$H.DE[H_single$Survive=="FALSE" & H_single$Group=="Train"],
                       H_single$H.DE[H_single$Survive=="TRUE" & H_single$Group=="Train"], curve=TRUE)
pr_test <- pr.curve(H_single$H.DE[H_single$Survive=="FALSE" & H_single$Group!="Train"],
                       H_single$H.DE[H_single$Survive=="TRUE" & H_single$Group!="Train"], curve=TRUE)

svg('Dec19/NewDataDec19_code/H1tp_PR.svg')
plot(pr_train, color="black", main="Single timepoint model", auc.main = FALSE)
plot(pr_test, color="red", add=TRUE)
dev.off()

sink('Dec19/NewDataDec19_code/H1tp_AUC.txt')
cat('ROC TRAIN\n')
roc_train
cat('\n\n\nROC_TEST\n')
roc_test
cat('\n\n\nPR_TRAIN\n')
pr_train
cat('\n\n\nPR_TEST\n')
pr_test
sink()


# barplots (Fig4F,G)
H_single$H1_temp <- H_single$H.DE - H.t
axislabels_H1tp <- c(-4, -2, 0, round(H.t,2), 4)
axisbreaks_H1tp <- axislabels_H1tp-H.t

H_barplot_group <- function(df, mygroup, plotvar, axlabels, axbreaks, mytitle){
  df <- df[mygroup,]
  acc <- sum(df$Prediction==df$Survive)/nrow(df)
  acc.str <- paste0('Accuracy = ', round(acc,2))
  df <- df[order(df[plotvar]),]
  df$Survive <- as.factor(df$Survive)
  df['Index'] <- c(1:nrow(df))
  ggplot(df, aes_string(x='Index', y=plotvar, fill='Survive'))+
    geom_bar(stat = "identity")+theme_classic()+
    scale_y_continuous(breaks=axbreaks, labels=axlabels)+
    geom_text(x=1, y=axbreaks[4]+0.5, label=acc.str, hjust=0)+
    labs(x=" ", y="Entropy", title = mytitle)
}
H_barplot_group(H_single, H_single$Group=="Train", 
                "H1_temp", axislabels_H1tp, axisbreaks_H1tp,
                "Single timepoint, Training set")
ggsave('Dec19/NewDataDec19_code/H1tp_Training_all.svg')

H_barplot_group(H_single, H_single$Group!="Train", 
                "H1_temp", axislabels_H1tp, axisbreaks_H1tp,
                "Single timepoint, Test set")
ggsave('Dec19/NewDataDec19_code/H1tp_Test_all.svg')


H_barplot_group(H_single, H_single$Group=="Train" & H_single$Time < 65, 
                "H1_temp", axislabels_H1tp, axisbreaks_H1tp,
                "Single timepoint, Training set, early timepoints")
ggsave('Dec19/NewDataDec19_code/H1tp_Training_early.svg')

H_barplot_group(H_single, H_single$Group!="Train"& H_single$Time < 65, 
                "H1_temp", axislabels_H1tp, axisbreaks_H1tp,
                "Single timepoint, Test set, early timepoints")
ggsave('Dec19/NewDataDec19_code/H1tp_Test_early.svg')


H_barplot_group(H_single, H_single$Group=="Train" & H_single$Time > 65, 
                "H1_temp", axislabels_H1tp, axisbreaks_H1tp,
                "Single timepoint, Training set, late timepoints")
ggsave('Dec19/NewDataDec19_code/H1tp_Training_late.svg')

H_barplot_group(H_single, H_single$Group!="Train"& H_single$Time > 65, 
                "H1_temp", axislabels_H1tp, axisbreaks_H1tp,
                "Single timepoint, Test set, late timepoints")
ggsave('Dec19/NewDataDec19_code/H1tp_Test_late.svg')

```


## Timecourse entropy - Model 1
This model uses variances across all genes
```{r}
get_entropy1_2tp <- function(myexpt){
  print(myexpt)
  short_expts <- c('T4_VNC', 'D39_GLY', 'D39_VAL', 'T4_GLY', 'T4_URA', 'T4_VAL', 'U-D39_URA', 'V-D39_VAL')
  if (myexpt %in% short_expts){
      thisexpt <- exptsheet[exptsheet$Experiment==myexpt & exptsheet$Time %in% c(30, 90), c('Time','RNAseqFile')]

  }else{
      thisexpt <- exptsheet[exptsheet$Experiment==myexpt & exptsheet$Time %in% c(30, 120), c('Time','RNAseqFile')]

  }
  thisRNAseq <- make_RNAseq_df('./',thisexpt)
  thisRNAonly <- as.matrix(thisRNAseq[complete.cases(thisRNAseq), grep('^l2FC', names(thisRNAseq))])
  
  n<- nrow(thisRNAonly)
  K <- cov(t(thisRNAonly))
  Hlist <- log(diag(K))
  H <- mean(Hlist)
  return(H)
}


x <- sapply(unique(exptsheet$Experiment), get_entropy1_2tp)
entropy_v1_2tp <- data.frame('Experiment' = unique(exptsheet$Experiment),
                                 'Entropy'=x)
entropy_v1_2tp <- merge(entropy_v1_2tp, exptsheet[,c('Experiment','Survive', 'Strain', 'AB', 'Adapted','Concentration', 'Group')], all.x=T, all.y=F)
entropy_v1_2tp <- unique(entropy_v1_2tp)

entropy_v1_2tp$Survive <- as.logical(entropy_v1_2tp$Survive)
entropy1_2tp_classifier <- threshold_classify(entropy_v1_2tp$Entropy[entropy_v1_2tp$Group=='Train'],
                                          as.factor(entropy_v1_2tp$Survive[entropy_v1_2tp$Group=='Train']))

H1_2tp.t <- entropy1_2tp_classifier$threshold
entropy_v1_2tp$Prediction <- entropy_v1_2tp$Entropy<H1_2tp.t

write.csv(entropy_v1_2tp, 'Dec19/NewDataDec19_code/H2tp_model1_predictions.csv', row.names=F)



# record threshold and confusion matrices
sink('Dec19/NewDataDec19_code/H2tp_model1_CMs.txt')
cat("Threshold: ")
cat(H1_2tp.t)
cat("\n\n\nTRAINING SET\n")
confusionMatrix(as.factor(entropy_v1_2tp$Prediction)[entropy_v1_2tp$Group=="Train"], 
                as.factor(entropy_v1_2tp$Survive[entropy_v1_2tp$Group=="Train"]), positive = "TRUE")
cat("\n\n\nTEST SET\n")
confusionMatrix(as.factor(entropy_v1_2tp$Prediction)[entropy_v1_2tp$Group!="Train"], 
                as.factor(entropy_v1_2tp$Survive[entropy_v1_2tp$Group!="Train"]), positive = "TRUE")
sink()



# ROC and PR curves
roc_train <- roc.curve(entropy_v1_2tp$Entropy[entropy_v1_2tp$Survive=="FALSE" & entropy_v1_2tp$Group=="Train"],
                       entropy_v1_2tp$Entropy[entropy_v1_2tp$Survive=="TRUE" & entropy_v1_2tp$Group=="Train"], curve=TRUE)
roc_test <- roc.curve(entropy_v1_2tp$Entropy[entropy_v1_2tp$Survive=="FALSE" & entropy_v1_2tp$Group!="Train"],
                       entropy_v1_2tp$Entropy[entropy_v1_2tp$Survive=="TRUE" & entropy_v1_2tp$Group!="Train"], curve=TRUE)

svg('Dec19/NewDataDec19_code/H2tp_model1_ROC.svg')
plot(roc_train, color="black", main="Multi-timepoint model 1", auc.main = FALSE)
plot(roc_test, color="red", add=TRUE)
dev.off()

pr_train <- pr.curve(entropy_v1_2tp$Entropy[entropy_v1_2tp$Survive=="FALSE" & entropy_v1_2tp$Group=="Train"],
                       entropy_v1_2tp$Entropy[entropy_v1_2tp$Survive=="TRUE" & entropy_v1_2tp$Group=="Train"], curve=TRUE)
pr_test <- pr.curve(entropy_v1_2tp$Entropy[entropy_v1_2tp$Survive=="FALSE" & entropy_v1_2tp$Group!="Train"],
                       entropy_v1_2tp$Entropy[entropy_v1_2tp$Survive=="TRUE" & entropy_v1_2tp$Group!="Train"], curve=TRUE)

svg('Dec19/NewDataDec19_code/H2tp_model1_PR.svg')
plot(pr_train, color="black", main="Multi-timepoint model 1", auc.main = FALSE)
plot(pr_test, color="red", add=TRUE)
dev.off()

sink('Dec19/NewDataDec19_code/H2tp_model1_AUC.txt')
cat('ROC TRAIN\n')
roc_train
cat('\n\n\nROC_TEST\n')
roc_test
cat('\n\n\nPR_TRAIN\n')
pr_train
cat('\n\n\nPR_TEST\n')
pr_test
sink()


# barplots (Fig4B,C,D)
entropy_v1_2tp$H1_temp <- entropy_v1_2tp$Entropy - H1_2tp.t
axislabels_H2tp_1 <- c(-6, -4, round(H1_2tp.t,2), -2, 0)
axisbreaks_H2tp_1 <- axislabels_H2tp_1-H1_2tp.t

H_barplot_group(entropy_v1_2tp, entropy_v1_2tp$Group=="Train", 
                "H1_temp", axislabels_H2tp_1, axisbreaks_H2tp_1,
                "Model 1, Training set")
ggsave('Dec19/NewDataDec19_code/H2tp_model1_Train.svg')
H_barplot_group(entropy_v1_2tp, entropy_v1_2tp$Group!="Train", 
                "H1_temp", axislabels_H2tp_1, axisbreaks_H2tp_1,
                "Model 1, Test set")
ggsave('Dec19/NewDataDec19_code/H2tp_model1_Test.svg')
```

## Timecourse entropy - Model 2
This model uses covarinaces across all genes
```{r}
get_entropy2_2tp <- function(myexpt){
  print(myexpt)
  short_expts <- c('T4_VNC', 'D39_GLY', 'D39_VAL', 'T4_GLY', 'T4_URA', 'T4_VAL', 'U-D39_URA', 'V-D39_VAL')
  if (myexpt %in% short_expts){
      thisexpt <- exptsheet[exptsheet$Experiment==myexpt & exptsheet$Time %in% c(30, 90), c('Time','RNAseqFile')]

  }else{
      thisexpt <- exptsheet[exptsheet$Experiment==myexpt & exptsheet$Time %in% c(30, 120), c('Time','RNAseqFile')]

  }
  thisRNAseq <- make_RNAseq_df('./',thisexpt)
  thisRNAonly <- as.matrix(thisRNAseq[complete.cases(thisRNAseq), grep('^l2FC', names(thisRNAseq))])
  n<- nrow(thisRNAonly)
  K <- cov(t(thisRNAonly))
  H <- determinant(K, logarithm=TRUE)$modulus
  return(H)
}


x <- sapply(unique(exptsheet$Experiment), get_entropy2_2tp)
entropy_v2_2tp <- data.frame('Experiment' = unique(exptsheet$Experiment),
                                 'Entropy'=x)
entropy_v2_2tp <- merge(entropy_v2_2tp, exptsheet[,c('Experiment','Survive', 'Strain', 'AB', 'Adapted','Concentration', 'Group')], all.x=T, all.y=F)
entropy_v2_2tp <- unique(entropy_v2_2tp)

entropy_v2_2tp$Survive <- as.logical(entropy_v2_2tp$Survive)
entropy2_2tp_classifier <- threshold_classify(entropy_v2_2tp$Entropy[entropy_v2_2tp$Group=='Train'],
                                          as.factor(entropy_v2_2tp$Survive[entropy_v2_2tp$Group=='Train']))

H2_2tp.t <- entropy2_2tp_classifier$threshold
entropy_v2_2tp$Prediction <- entropy_v2_2tp$Entropy<H2_2tp.t

write.csv(entropy_v2_2tp, 'Dec19/NewDataDec19_code/H2tp_model2_predictions.csv', row.names=F)



# record threshold and confusion matrices
sink('Dec19/NewDataDec19_code/H2tp_model2_CMs.txt')
cat("Threshold: ")
cat(H2_2tp.t)
cat("\n\n\nTRAINING SET\n")
confusionMatrix(as.factor(entropy_v2_2tp$Prediction)[entropy_v2_2tp$Group=="Train"], 
                as.factor(entropy_v2_2tp$Survive[entropy_v2_2tp$Group=="Train"]), positive = "TRUE")
cat("\n\n\nTEST SET\n")
confusionMatrix(as.factor(entropy_v2_2tp$Prediction)[entropy_v2_2tp$Group!="Train"], 
                as.factor(entropy_v2_2tp$Survive[entropy_v2_2tp$Group!="Train"]), positive = "TRUE")
sink()



# ROC and PR curves
roc_train <- roc.curve(entropy_v2_2tp$Entropy[entropy_v2_2tp$Survive=="FALSE" & entropy_v2_2tp$Group=="Train"],
                       entropy_v2_2tp$Entropy[entropy_v2_2tp$Survive=="TRUE" & entropy_v2_2tp$Group=="Train"], curve=TRUE)
roc_test <- roc.curve(entropy_v2_2tp$Entropy[entropy_v2_2tp$Survive=="FALSE" & entropy_v2_2tp$Group!="Train"],
                       entropy_v2_2tp$Entropy[entropy_v2_2tp$Survive=="TRUE" & entropy_v2_2tp$Group!="Train"], curve=TRUE)

svg('Dec19/NewDataDec19_code/H2tp_model2_ROC.svg')
plot(roc_train, color="black", main="Multi-timepoint model 2", auc.main = FALSE)
plot(roc_test, color="red", add=TRUE)
dev.off()

pr_train <- pr.curve(entropy_v2_2tp$Entropy[entropy_v2_2tp$Survive=="FALSE" & entropy_v2_2tp$Group=="Train"],
                       entropy_v2_2tp$Entropy[entropy_v2_2tp$Survive=="TRUE" & entropy_v2_2tp$Group=="Train"], curve=TRUE)
pr_test <- pr.curve(entropy_v2_2tp$Entropy[entropy_v2_2tp$Survive=="FALSE" & entropy_v2_2tp$Group!="Train"],
                       entropy_v2_2tp$Entropy[entropy_v2_2tp$Survive=="TRUE" & entropy_v2_2tp$Group!="Train"], curve=TRUE)

svg('Dec19/NewDataDec19_code/H2tp_model2_PR.svg')
plot(pr_train, color="black", main="Multi-timepoint model 2", auc.main = FALSE)
plot(pr_test, color="red", add=TRUE)
dev.off()

sink('Dec19/NewDataDec19_code/H2tp_model2_AUC.txt')
cat('ROC TRAIN\n')
roc_train
cat('\n\n\nROC_TEST\n')
roc_test
cat('\n\n\nPR_TRAIN\n')
pr_train
cat('\n\n\nPR_TEST\n')
pr_test
sink()


# barplots (Fig4B,C,D)
entropy_v2_2tp$H2_temp <- entropy_v2_2tp$Entropy - H2_2tp.t
axislabels_H2tp_2 <- c(-90000,-87500, -85000, round(H2_2tp.t,2), -80000,-77500)
axisbreaks_H2tp_2 <- axislabels_H2tp_2-H2_2tp.t

H_barplot_group(entropy_v2_2tp, entropy_v2_2tp$Group=="Train", 
                "H2_temp", axislabels_H2tp_2, axisbreaks_H2tp_2,
                "Model 2, Training set")
ggsave('Dec19/NewDataDec19_code/H2tp_model2_Train.svg')
H_barplot_group(entropy_v2_2tp, entropy_v2_2tp$Group!="Train", 
                "H2_temp", axislabels_H2tp_2, axisbreaks_H2tp_2,
                "Model 2, Test set")
ggsave('Dec19/NewDataDec19_code/H2tp_model2_Test.svg')
```

## Timecourse entropy - Model 3
This model uses covariances, but after regularization of the inverse covariance matrix. 
The regularization is done on a server. Here, we read in the data and pick the regularization level that gives the best prediction on the training set. 
```{r}
entropy_v3_2tp <- read.csv('Dec19/NewDataDec19_code/Entropy/entropy_4_1219.csv', header=T, stringsAsFactors = F)
lams <- seq(5,0,-0.05)

Ent_v3_summary <- data.frame()
for (rhoval in lams){
  tryCatch({
    entropy_v3_2tp_output <- entropy_v3_2tp[entropy_v3_2tp$Rho==rhoval,]
    entropy_v3_2tp_output <- merge(entropy_v3_2tp_output, exptsheet[,c('Experiment', 'Survive', 'Group')], by="Experiment", all.x=T, all.y=F, sort=F)
    
    entropy_v3_2tp_train <- entropy_v3_2tp_output[entropy_v3_2tp_output$Group=='Train',]
    entropy_v3_2tp_train <- unique(entropy_v3_2tp_train)
    entropy_v3_2tp_train <- entropy_v3_2tp_train[complete.cases(entropy_v3_2tp_train),]
    #entropy_v3_2tp_test <- entropy_v3_2tp_output[entropy_v3_2tp_output$Group!='Train',]
    H_clf <- threshold_classify(entropy_v3_2tp_train$H_pdON, as.factor(as.logical(entropy_v3_2tp_train$Survive)))
    x <- as.data.frame(t(as.data.frame(H_clf$cm$overall)))
    x$Rho <- rhoval
    x$Threshold <- H_clf$threshold
    Ent_v3_summary <- rbind(Ent_v3_summary, x)
  }, error = function(e){print(e)})

}

bestrho <- Ent_v3_summary$Rho[which.max(Ent_v3_summary$Accuracy)]
ggplot(Ent_v3_summary, aes(x=Rho, y=Accuracy))+geom_line()+theme_bw()+labs(y="Training Set Accuracy")+
  geom_vline(xintercept = bestrho, col='red',linetype = "dashed" )
ggsave('Dec19/NewDataDec19_code/Entropy/Accuracy_vs_Rho.svg')


write.csv(Ent_v3_summary,'Dec19/NewDataDec19_code/Entropy/H2tp_model3_rho_vs_performance.csv', row.names = F)




entropy_v3_2tp_best <- entropy_v3_2tp[entropy_v3_2tp$Rho==bestrho,]
# drop NAs
entropy_v3_2tp_best <- entropy_v3_2tp_best[complete.cases(entropy_v3_2tp_best),]

entropy_v3_2tp_best <- merge(entropy_v3_2tp_best, exptsheet[,c('Experiment','Survive', 'Strain', 'AB', 'Adapted','Concentration', 'Group')], all.x=T, all.y=F)
entropy_v3_2tp_best <- unique(entropy_v3_2tp_best)

entropy_v3_2tp_best$Survive <- as.logical(entropy_v3_2tp_best$Survive)
entropy_v3_2tp_best_classifier <- threshold_classify(entropy_v3_2tp_best$H_pdON[entropy_v3_2tp_best$Group=='Train'],
                                          as.factor(entropy_v3_2tp_best$Survive[entropy_v3_2tp_best$Group=='Train']))

H3_2tp.t <- entropy_v3_2tp_best_classifier$threshold
entropy_v3_2tp_best$Prediction <- entropy_v3_2tp_best$H_pdON<H3_2tp.t

write.csv(entropy_v3_2tp_best, 'Dec19/NewDataDec19_code/Entropy/H2tp_model3_predictions.csv', row.names=F)



# record threshold and confusion matrices
sink('Dec19/NewDataDec19_code/Entropy/H2tp_model3_CMs.txt')
cat("Threshold: ")
cat(H3_2tp.t)
cat("\n\n\nTRAINING SET\n")
confusionMatrix(as.factor(entropy_v3_2tp_best$Prediction)[entropy_v3_2tp_best$Group=="Train"], 
                as.factor(entropy_v3_2tp_best$Survive[entropy_v3_2tp_best$Group=="Train"]), positive = "TRUE")
cat("\n\n\nTEST SET\n")
confusionMatrix(as.factor(entropy_v3_2tp_best$Prediction)[entropy_v3_2tp_best$Group!="Train"], 
                as.factor(entropy_v3_2tp_best$Survive[entropy_v3_2tp_best$Group!="Train"]), positive = "TRUE")
sink()



# ROC and PR curves
roc_train <- roc.curve(entropy_v3_2tp_best$H_pdON[entropy_v3_2tp_best$Survive=="FALSE" & entropy_v3_2tp_best$Group=="Train"],
                       entropy_v3_2tp_best$H_pdON[entropy_v3_2tp_best$Survive=="TRUE" & entropy_v3_2tp_best$Group=="Train"], curve=TRUE)
roc_test <- roc.curve(entropy_v3_2tp_best$H_pdON[entropy_v3_2tp_best$Survive=="FALSE" & entropy_v3_2tp_best$Group!="Train"],
                       entropy_v3_2tp_best$H_pdON[entropy_v3_2tp_best$Survive=="TRUE" & entropy_v3_2tp_best$Group!="Train"], curve=TRUE)

svg('Dec19/NewDataDec19_code/Entropy/H2tp_model3_ROC.svg')
plot(roc_train, color="black", main="Multi-timepoint model 3", auc.main = FALSE)
plot(roc_test, color="red", add=TRUE)
dev.off()

pr_train <- pr.curve(entropy_v3_2tp_best$H_pdON[entropy_v3_2tp_best$Survive=="FALSE" & entropy_v3_2tp_best$Group=="Train"],
                       entropy_v3_2tp_best$H_pdON[entropy_v3_2tp_best$Survive=="TRUE" & entropy_v3_2tp_best$Group=="Train"], curve=TRUE)
pr_test <- pr.curve(entropy_v3_2tp_best$H_pdON[entropy_v3_2tp_best$Survive=="FALSE" & entropy_v3_2tp_best$Group!="Train"],
                       entropy_v3_2tp_best$H_pdON[entropy_v3_2tp_best$Survive=="TRUE" & entropy_v3_2tp_best$Group!="Train"], curve=TRUE)

svg('Dec19/NewDataDec19_code/Entropy/H2tp_model3_PR.svg')
plot(pr_train, color="black", main="Multi-timepoint model 3", auc.main = FALSE)
plot(pr_test, color="red", add=TRUE)
dev.off()

sink('Dec19/NewDataDec19_code/Entropy/H2tp_model3_AUC.txt')
cat('ROC TRAIN\n')
roc_train
cat('\n\n\nROC_TEST\n')
roc_test
cat('\n\n\nPR_TRAIN\n')
pr_train
cat('\n\n\nPR_TEST\n')
pr_test
sink()


# barplots (Fig4B,C,D)
entropy_v3_2tp_best$H3_temp <- entropy_v3_2tp_best$H_pdON - H3_2tp.t
axislabels_H2tp_3 <- c(1000,1100, 1200, round(H3_2tp.t,2), 1400,1500)
axisbreaks_H2tp_3 <- axislabels_H2tp_3-H3_2tp.t

H_barplot_group(entropy_v3_2tp_best, entropy_v3_2tp_best$Group=="Train", 
                "H3_temp", axislabels_H2tp_3, axisbreaks_H2tp_3,
                "Model 3, Training set")
ggsave('Dec19/NewDataDec19_code/Entropy/H2tp_model3_Train.svg')
H_barplot_group(entropy_v3_2tp_best, entropy_v3_2tp_best$Group!="Train", 
                "H3_temp", axislabels_H2tp_3, axisbreaks_H2tp_3,
                "Model 3, Test set")
ggsave('Dec19/NewDataDec19_code/Entropy/H2tp_model3_Test.svg')
```


Save all data
```{r}
save.image('Dec19/NewDataDec19_code/Entropy.RData')
```